Trade Reviews

### 2019-04-06 tradeReview.Rmd
Added get all team rosters method for yahoo api

#### Fantasy team rosters
```{r}
source("R/yahoo_api.R")
league_string <- paste0("388.l.",Sys.getenv("LEAGUE_KEY"))
get_team_roster(league_string, 8) %>% 
  clean_names() %>% 
  mutate(owner = 'Tom',
         name_full = chartr("áéóíñú", "aeoinu", name_full)) -> my_team
get_team_roster(league_string, 3) %>% 
  clean_names() %>% 
  mutate(owner = 'Chris',
         name_full = chartr("áéóíñú", "aeoinu", name_full)) -> chris_team

my_team %>% 
  bind_rows(chris_team) %>% 
  select(owner, name_full, display_position) -> roster_players

@@

trade_df %>% 
  mutate(z_sum = round(z_sum)) %>% 
  arrange(z_sum %>% desc, pick) %>% 
  View()
```

>>>>

#### Fantasy team rosters
```{r}
source("R/yahoo_api.R")
league_string <- paste0("388.l.",Sys.getenv("LEAGUE_KEY"))
get_team_rosters(league_string) -> rosters

rosters %>% 
  filter(grepl('Tom|Christopher',manager)) %>% 
  select(manager, name_full, display_position) -> roster_players

@@

trade_df %>% 
  mutate(z_sum = round(z_sum)) %>% 
  arrange(z_sum %>% desc, pick) %>% 
  write_csv("data/tradeReview_20190405.csv")
```
